\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-10-18 paper/manuscript.tex
forgot to actually add the LA plots and tables to the manuscript

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words, according to the informed Dirichlet model of Monroe et al. (2008).}
	\label{fightinwords}
	\includegraphics[width=\linewidth]{figures/fightinWords.png}
\end{figure}

@@

>>>>

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Indiana), according to the informed Dirichlet model of Monroe et al. (2008).}
	\label{fightinwords}
	\includegraphics[width=\linewidth]{figures/fightinWords.png}
\end{figure}

%fightin words results
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Top democratic and Republican words (Louisiana), according to the informed Dirichlet model of Monroe et al. (2008).}
	\label{fightinwordsLA}
	\includegraphics[width=\linewidth]{figures/fightinWordsLA.png}
\end{figure}

@@

%Partisan top words - topic model
\input{tables/partisanTopWordsLA.tex}

%Partisan top words - fightin words
\input{tables/fightinwordsLA.tex}
